---
title: "MA615 HW1 ZBY"
author: "zby"
date: "9/23/2021"
output:
  pdf_document: default
  html_document: default
---

1.What adjustment is needed?
 We should run "library(esquisse)" and "esquisser(data = mtcars_mpg2, viewer = "browser")"
2. In the first picture,  the smooth line and points indicated that the value of mpg gets peak when disp is 400. And the smooth line fitted these points well.
3. From the boxplot, we can learn the minimum, 25th percentile, 75th percentile and the maximum of cyl. 
4. I realized that GitHub is a web-based collaboration tool based on the git source control package.I learned how to connect Github with R studio. I learned how to pull, push and commit.

```{r}
## document_car_viz.R
library(tidyverse)

# call built-in data mtcars.
data(mtcars)

# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]


# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]

# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
source(file = "hand_functions.R", echo = TRUE)

# Now use the function from hand_functions.R

sp_out <- sum_special(mtcars_mpg2)


# library(esquisse)
# 
# esquisser(data = mtcars_mpg2, viewer = "browser")



ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()


# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?


ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")
```

```{r}
##document_hand_functions.R
sum_special <- function(df_x){
  
  ## sum_special calculates data summary statistics
  ## the input param df_x is the data frame of input values
  
  #  browser()  # browser() will start the debugger
               # if the line is uncommented
  
  
  ## test the input data to assure that it is a data frame.
  try(if(!is.data.frame(df_x)) stop("Input data must be a data frame."))
  
  
  sp_means <- apply(df_x, MARGIN = 2, FUN = mean)
  sp_var <- apply(df_x, MARGIN = 2, FUN = var)
  sp_cov <- cov(df_x)
  sp_cor <- cor(df_x)
  
  ## Note that defining a list with the 
  ## syntax list(list_name = list_content) produces
  ## named list items
  sp_outputs <- list(sp_means=sp_means, 
                     sp_var = sp_var, 
                     sp_cov = sp_cov, 
                     sp_cor = sp_cor)
  
  return(sp_outputs)
}

```